Type cones of $\b{g}$-vector fans

### 2019-02-08 thirdPaper/draft/typeConeAssociahedra.tex
figure cluster fans

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

\para{The $\b{g}$-vector fan and generalized associahedron}
%
The following statement is well known.
\vincent{Explain}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

\para{The $\b{g}$-vector fan and generalized associahedron}
%
The following statement is well known.
\vincent{Explain}
Examples are illustrated in \cref{fig:clusterFans}.

\begin{figure}[h]
	\capstart
	%\centerline{\includegraphics[scale=.45]{clusterFans}}
	\centerline{
	\begin{overpic}[scale=.45]{clusterFans}
	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
	\end{overpic}
	}
  \caption{Two $\b{g}$-vector fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{HohlwegPilaudStella}.}
	\label{fig:clusterFans}
\end{figure}
